KidsAIR: merge health datasets

### 2020-06-17 dustrak_data_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

# Join PM data with linked IDs and make new variables for spikes in PM
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_pm <- 
  read_rds(paste0(output_path, "Output/kids_pm_new4.rds")) 
kids_linked_ids <- 
  read_rds(paste0(output_path, "Output/kids_linked_ids.rds"))

@@

# Save dataset
```{r}
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

write_rds(kids_pm_new5, paste0(output_path, "Output/pm_clean.rds"))
```

>>>>

---
title: "KidsAIR initial PM data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 16 June 2020"
output: pdf_document
---

@@

# Join PM data with linked IDs and make new variables for spikes in PM
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_pm <- 
  read_rds(paste0(file_path, "Output/kids_pm_new4.rds")) 
kids_linked_ids <- 
  read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

# Save dataset
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

write_rds(kids_pm_new5, paste0(file_path, "Output/pm_clean.rds"))
```

### 2020-06-17 home_child_data_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 12 May 2020"
output: pdf_document
---

@@

# Load files 
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > child.xlsx
wmt_child_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_child_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > home.xlsx
wmt_home_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_home_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > homewinter.xlsx
wmt_homewinter_initial <- read_xlsx(paste0(file_path, "Input/WMT/wmt_homewinter_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > WMT > Home Data > parentdemographics.xlsx
wmt_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/WMT/wmt_parent_demographics_20191126.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

# Load, format, and save home and child overview/demographic data for NN
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > child.xlsx
nn_child_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_child_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         child_id_char = gsub(child_id_char, pattern = " ", replacement = ""),
         child_id_char = gsub(child_id_char, pattern = "_", replacement = ""),
         child_id_char = gsub(child_id_char, pattern = "-", replacement = ""),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > home.xlsx
nn_home_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_home_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > homewinter.xlsx
nn_homewinter_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_homewinter_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = if_else(home_id == 62 | home_id == 45, winter_id + 1, winter_id),
         winter_id = as.character(winter_id)) %>% 
  filter(winter_id == 1 | winter_id ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > Home Data > parentdemographics.xlsx
nn_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/NN/nn_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

# Load, format, and save home and child overview/demographic data for AK
```{r}
# Load files 
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > child.xlsx
ak_child_initial <- read_xlsx(paste0(file_path, "Input/AK/ak_child_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > home.xlsx
ak_home_initial <- read_xlsx(paste0(file_path, "Input/AK/ak_home_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > homewinter.xlsx
ak_homewinter_initial <- read_xlsx(paste0(file_path, "Input/AK/ak_homewinter_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > Home Data > parentdemographics.xlsx
ak_parent_demographics_initial <-
  read_xlsx(paste0(file_path, "Input/AK/ak_parent_demographics_20191216.xlsx")) %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # distinct homes in database = 360
  filter(!is.na(child_id_num)) %>% 
  # distinct(area, child_id_num, .keep_all = TRUE) %>%  # distinct kids in database = 512
  # distinct(area, home_id, .keep_all = TRUE) %>% # distinct homes with kids in databse = 340
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(!is.na(treatment)) %>%  
  distinct(area, child_id_num, .keep_all = TRUE) %>%   # distinct kids with treatment = 512
  distinct(area, home_id, .keep_all = TRUE)  # distinct homes with kids with treatment = 340
```

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%  
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # enrolled homes in database = 360
  filter(!is.na(treatment)) %>% 
  # distinct(area, home_id)  # randomized homes with treatment assignment = 342
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>% 
  #distinct(area, home_id)  # randomized homes with treatment assignment = 340
  ungroup() %>% 
  arrange(area, home)

@@

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  filter(!is.na(child_id_num)) %>% 
  filter(!is.na(treatment)) %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash) %>% 
  ungroup() %>% 
  arrange(area, home, child_id_char)

write_rds(kids_demographics, paste0(file_path, "Output/kids_combined_demographics.rds"))
```

>>>>

---
title: "KidsAIR initial home/child data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 16 June 2020"
output: pdf_document
---

@@

# Load files 
## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > child
wmt_child_initial <- read_csv(paste0(file_path, "Input/WMT/child.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > home
wmt_home_initial <- read_csv(paste0(file_path, "Input/WMT/home.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > homewinter
wmt_homewinter_initial <- read_csv(paste0(file_path, "Input/WMT/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > WMT > Home Data > parentdemographics
wmt_parent_demographics_initial <-
  read_csv(paste0(file_path, "Input/WMT/parentdemographics.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

# Load, format, and save home and child overview/demographic data for NN
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > child
nn_child_initial <- read_xlsx(paste0(file_path, "Input/NN/child.xlsx"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         child_id_char = gsub(child_id_char, pattern = " ", replacement = ""),
         child_id_char = gsub(child_id_char, pattern = "_", replacement = ""),
         child_id_char = gsub(child_id_char, pattern = "-", replacement = ""),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > home
nn_home_initial <- read_xlsx(paste0(file_path, "Input/NN/home.xlsx"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > homewinter
nn_homewinter_initial <- read_csv(paste0(file_path, "Input/NN/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = as.character(winter_id)) %>% 
  filter(winter_id == 1 | winter_id ==2) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > Navajo > Home Data > parentdemographics
nn_parent_demographics_initial <-
  read_csv(paste0(file_path, "Input/NN/parentdemographics.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

# Load, format, and save home and child overview/demographic data for AK
```{r}
# Load files 
## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > child
ak_child_initial <- read_xlsx(paste0(file_path, "Input/AK/child.xlsx"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  # filter(enrolled == 1) %>% # filter out kids who weren't enrolled
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > home
ak_home_initial <- read_xlsx(paste0(file_path, "Input/AK/home.xlsx"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > homewinter
ak_homewinter_initial <- read_csv(paste0(file_path, "Input/AK/homewinter.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  filter(winterid != 3) %>% # filter for winterid == 1 or 2. What about missing intervention date?
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)

## Box location: All Files > NoonGroupData > KidsAIR > 
## FINAL DATA SETS > AK > Home Data > parentdemographics
ak_parent_demographics_initial <-
  read_csv(paste0(file_path, "Input/AK/parentdemographics.csv"), na = "NULL") %>% 
  rename_all(tolower) %>% 
  #filter(whatmissing != "all" | is.na(whatmissing)) %>%  # filter out if missing == "all"
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five)

@@

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # distinct homes in database = 390
  filter(!is.na(child_id_num)) %>% 
  # distinct(area, child_id_num, .keep_all = TRUE) %>%  # distinct kids in database = 512
  # distinct(area, home_id, .keep_all = TRUE) %>% # distinct homes with kids in databse = 340
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(!is.na(treatment)) %>%  
  distinct(area, child_id_num, .keep_all = TRUE) %>%   # distinct kids with treatment = 512
  distinct(area, home_id, .keep_all = TRUE)  # distinct homes with kids with treatment = 340
```

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  mutate(home = gsub("_", "", home)) %>% 
  mutate(home = gsub("-", "", home)) %>% 
  mutate(home = gsub(" ", "", home)) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%  
  mutate(home_id = as.character(home_id)) %>% 
  # distinct(area, home_id)  # enrolled homes in database = 360
  filter(!is.na(treatment)) %>% 
  filter(winter_id != 99) %>% 
  # distinct(area, home_id)  # randomized homes with treatment assignment = 342
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>% 
  #distinct(area, home_id)  # randomized homes with treatment assignment = 340
  ungroup() %>% 
  arrange(area, home)

@@

ak_demographics <- read_rds(paste0(file_path, "Output/ak_demographic_data.rds")) %>% 
  mutate(intervention_date = mdy(intervention_date))
nn_demographics <- read_rds(paste0(file_path, "Output/nn_demographic_data.rds")) %>% 
  mutate(intervention_date = mdy(intervention_date))
wmt_demographics <- read_rds(paste0(file_path, "Output/wmt_demographic_data.rds")) %>% 
  mutate(intervention_date = ymd(intervention_date))

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  mutate(home = gsub("_", "", home)) %>% 
  mutate(home = gsub("-", "", home)) %>% 
  mutate(home = gsub(" ", "", home)) %>% 
  mutate(home_id = as.numeric(home_id)) %>% 
  filter(home_id < 1000) %>%
  mutate(home_id = as.character(home_id)) %>% 
  filter(!is.na(child_id_num)) %>% 
  filter(!is.na(treatment)) %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  ungroup() %>% 
  arrange(area, home, child_id_char)

write_rds(kids_demographics, paste0(file_path, "Output/demographics_clean.rds"))
```

# Check observations against documented reasons for dropping from study
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

demographics_initial <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))

# Checking observations against drop reasons from "KidsAIR reasons for dropping" excel file
# Filter out observations below when participants had dropped and should not be in dataset
demographics_check <- demographics_initial %>% 
  filter(area == "AK") %>% 
  arrange(home, child_id_char)

# dropped before winter 1 - filter out
filter_out_wmt <- c("WMA227", "WMA254", "WMA337", "WMA600", "WMA601")
# missing winter 2 demographic data but had not dropped - don't filter out
keep_winter_2_wmt <- c("WMA407", "WMA497", "WMA509")
# NN homes with missing data but had not dropped - don't filter out
keep_nn <- c("CH110", "TC359", "TC452", "TC453")

demographics_new <- demographics_initial %>% 
  filter(!home %in% filter_out_wmt) %>% 
  mutate(keep_var_wmt = if_else(home %in% keep_winter_2_wmt & winter_id == 2, 1, 0),
         filter_var_wmt = if_else(area == "WMT" & keep_var_wmt == 0 & winter_id == 2 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_wmt == 0) %>% 
  filter(home != "CH105") %>% 
  mutate(keep_var_nn = if_else(home %in% keep_nn, 1, 0),
         filter_var_nn = if_else(area == "NN" & keep_var_nn == 0 & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_nn == 0) %>% 
  filter(home != "YKC19102") %>% 
  filter(home != "YKC19104") %>% 
  mutate(filter_var_ak = if_else(area == "AK" & is.na(gender_parent), 1, 0)) %>% 
  filter(filter_var_ak == 0) %>%
  mutate(treatment_assigned = as.character(treatment),
         treatment_actual = as.character(treatment),
         treatment_assigned = if_else(treatment == "Placebo - TX Education", "Placebo", treatment_actual)) %>% 
  select(-treatment, -filter_var_wmt, -keep_var_wmt, -filter_var_nn, 
         -keep_var_nn, -filter_var_ak)

write_rds(demographics_new, paste0(file_path, "Output/demographics_final.rds"))

kids_linked_ids_new <- demographics_new %>% 
  select(area, home, home_id, winter_id, home_winter_id, treatment_assigned, treatment_actual) %>% 
  distinct(area, home, winter_id, .keep_all = TRUE)

write_rds(kids_linked_ids_new, paste0(file_path, "Output/kids_linked_ids_final.rds"))
```

### 2020-06-17 manuscript_tables_figures.Rmd
data cleaning updates

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_initial <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))

@@

```{r}
# number of placebo households, total and by area
placebo_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>%
  count(area)
placebo_homes

>>>>

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

demographics_initial <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))

@@

```{r}
# number of placebo households, total and by area
placebo_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  filter(area == "WMT") %>% 
  select(area, home, home_id, winter_id, home_winter_id, treatment)
  #filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>%
  count(area)
placebo_homes

### 2020-06-17 merge_health_datasets.Rmd
data cleaning updates

# Initial data merge - long format
```{r}
health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_mean_temp) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

@@

health_merged5 <- health_merged4 %>% 
  left_join(kids_medical_records, by = c("area", "home", "home_winter_id", "winter_id", 
                                      "child_id_num", "treatment")) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, sample_date, sampling_day, at_home_location, 
         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:med_rec_comments) %>% 
  ungroup()

health_merged6 <- health_merged5 %>% 
  left_join(kids_lrti, by = c("area", "home", "home_winter_id", "winter_id", 
                                      "child_id_num", "treatment")) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, sample_date, sampling_day, at_home_location, 
         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:lrti_professional_comments) %>% 
  ungroup()

write_rds(health_merged6, paste0(output_path, "Output/health_data_merged.rds"))
write_csv(health_merged6, paste0(output_path, "Output/health_data_merged.csv"))
```

>>>>

# Initial data merge - long format
```{r}
health_merged1 <- kids_csq %>% 
  select(-home_id) %>% 
  mutate(visit_date = csq_date) %>% 
  full_join(kids_med_visit, by = c("area", "home", "home_winter_id", "treatment",
                                   "winter_id", "child_id_num", "visit_date")) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, csq_date:med_visit_mean_temp) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  distinct(child_id_num, visit_date, .keep_all = TRUE) %>% 
  ungroup()

@@

#health_merged5 <- health_merged4 %>% 
# left_join(kids_medical_records, by = c("area", "home", "home_winter_id", "winter_id", 
#                                      "child_id_num", "treatment")) %>% 
#  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
#  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
#         treatment, sample_date, sampling_day, at_home_location, 
#         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:med_rec_comments) %>% 
#  ungroup()

health_merged5 <- health_merged4 %>% 
  left_join(kids_lrti, by = c("area", "home", "home_winter_id", "winter_id", 
                                      "child_id_num", "treatment")) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, sample_date, sampling_day, at_home_location, 
         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:lrti_professional_comments) %>% 
  ungroup()

write_rds(health_merged5, paste0(output_path, "Output/health_data_merged.rds"))
write_csv(health_merged5, paste0(output_path, "Output/health_data_merged.csv"))
```
